Stat 400 Project

### 2021-12-07 Stat 400 proj.Rmd
Started creating a bootstrap function for each individual day

```{r}

#create starting positions and state function
starting_vals <- function(num_subjects, I_0, x_dim, y_dim){

@@

#Testing
df <- starting_vals(1000, 2, 1, 1)
len <- get_step_length(df, 1, 1)
dir <- get_step_direction(len)
delts <- get_delts(len, dir)
newdf <- update_coords(df, delts)
coords <- coord_checker(df, newdf, 1, 1)
coords
new_status <- infection_status(coords, 8)
new_status
print(new_status[,4])

@@

plot <- ggplot() +
  geom_line(aes(x=x, y=y)) +
  xlab('Day') +
  ylab('Number of Cases') +
  ggtitle('Number of Covid-19 cases over time')

#bootstrap

mean_func <- function(x, idx) {
  mean(x[idx])
}

>>>>

```{r}
#create starting positions and state function
starting_vals <- function(num_subjects, I_0, x_dim, y_dim){

@@

#Testing
df <- starting_vals(1000, 2, 1, 1)
len <- get_step_length(df, 1, 1)
dir <- get_step_direction(len)
delts <- get_delts(len, dir)
newdf <- update_coords(df, delts)
coords <- coord_checker(df, newdf, 1, 1)
coords
new_status <- infection_status(coords, 8)
new_status

@@

ggplot() +
  geom_line(aes(x=x, y=y)) +
  xlab('Day') +
  ylab('Number of Cases') +
  ggtitle('Number of Covid-19 cases over time')

#bootstrap
mean_func <- function(daytuh, idx) {
  mean(daytuh[idx])
}

get_bootstrap_cis <- function(days, num_subjects, x_dim, y_dim, I_0, inf_dist, sample_size, ci_type='perc'){
  #Create data frame to store samples
  samps <- matrix(data=NA, nrow=sample_size, ncol=days + 1)
  samps <- data.frame(samps)

  #Create data frame to store confidence intervals
  ci_df <- matrix(data=NA, nrow=days + 1, ncol=2)
  ci_df <- data.frame(ci_df)

  for(i in 1:sample_size){
    samps[i, ] <- simulator(days, num_subjects, x_dim, y_dim, I_0, inf_dist)
  }

  for(i in 1:ncol(samps)){
    #Make sure column has more than one unique value
    check <- (length(unique(samps[ ,i])) != 1)
    if(check){
    boot_obj <- boot(samps[ ,i], mean_func, 2000)
    ci_obj <- boot.ci(boot_obj, conf = .95, type = ci_type)
    ci_df[i, ] <- c(ci_obj$percent[4], ci_obj$percent[5])
    }else{ci_df[i, ] <- c(samps[1, i], samps[1, i])}
  }
return(ci_df)
}

get_bootstrap_cis(days=50, num_subjects=100, x_dim=10, y_dim=10, I_0=2, inf_dist=1, sample_size=5)
